Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
fix refs
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

First, we describe existing techniques for adapting storage systems
(\S\ref{sec:evidence}). Next, we discuss the ``distributed systems'' inspired
abstractions employed by Ceph (\S\ref{background}) and allude to their
re-usability as components in other services. The next section
enumerates the abstractions that Malacology exposes in the
implementation section (\S\ref{implementation}). We then show how we use
Malacology to synthesize entirely new storage services on an existing
system through configuration and small changes (\S\ref{services}). We
conclude by evaluating real-world use cases (\S\ref{evaluation}).

@@

\subsection{Cluster State Management}
\label{consistencyversioning-of-cluster-state}

@@

\paragraph*{Malacology:} The implementation of Ceph's object abstraction,
although powerful, has some drawbacks. Supporting only C/C++ for object
interface developers, Ceph requires distribution of compiled binaries for the
correct architecture, adding a large barrier of entry for developers and
system administrators. Second, having no way to dynamically unload modules,
any changes require a full restart of an OSD which may have serious
performance impacts due to a loss of cached data~\cite{facebook-mysql}. And
finally, the security limitations of the framework limit the use of object
classes to all but those with administrative level access and deep technical
expertise.

To address these concerns, Malacology takes advantage of community contributed
Lua extensions to Ceph allowing new object interfaces to be dynamically loaded
into the system and modified at runtime, resulting in a object storage API
with economy of expression, which at the same time provides the full set of
features of the base object class~\cite{bdmc}. New object interfaces that are
expressed in thousands of lines of code can be implemented in approximately an
order of magnitude less code~\cite{geambasu_comet_2010}.

@@

\section{Services Built on Malacology}\label{services-built-on-malacology}

@@

In Section~\cite{evaluation} we quantify the trade-offs of throughput and
latency for an approach based on a round-robin batching mode, and compare this
mode to one in which the metadata server mediates access to the sequencer
state when in it is being shared among multiple clients.

@@

\section{Evaluation}\label{evaluation}
We have conducted our evaluation on CloudLab as well as our own 20 node cluster. We follow the ``Popper Convention"~\cite{anonymous} so as to try and make our experiments as reproducible as possible. We have a GitHub repository with our source code,  experimental environment, configuration parameters, and workloads in a GitHub repository. Due to the double-blind policy, we have temporarily disabled the links to our graphs and experimental details.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{The sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput.png}
migrates to a new MDS immediately because its uses a policy designed for bursty
workloads. This is a trace of the same workload running twice: once with a
single MDS and once with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}

>>>>

The remainder of this paper is structured as follows. First we describe
Malacology by presenting the subsystems within Ceph that we re-purpose, and
briefly describe how those system are used within Malacology
(\S\ref{sec:malacology}). Next we describe the services that we have
constructed within the Malacology framework (\S\ref{sec:services}),
and evaluate our ideas within our prototype implementation
(\S\ref{evaluation}). Finally we discuss related work and conclude.

@@

\subsection{Cluster State Management}
\label{sec:mon}
\label{consistencyversioning-of-cluster-state}

@@

\paragraph*{Malacology:} The implementation of Ceph's object abstraction,
although powerful, has some drawbacks. Supporting only C/C++ for object
interface developers, Ceph requires distribution of compiled binaries for the
correct architecture, adding a large barrier of entry for developers and
system administrators. Second, having no way to dynamically unload modules,
any changes require a full restart of an OSD which may have serious
performance impacts due to a loss of cached data. And
finally, the security limitations of the framework limit the use of object
classes to all but those with administrative level access and deep technical
expertise.

To address these concerns, Malacology takes advantage of community contributed
Lua extensions to Ceph allowing new object interfaces to be dynamically loaded
into the system and modified at runtime, resulting in a object storage API
with economy of expression, which at the same time provides the full set of
features of the base object class. New object interfaces that are
expressed in thousands of lines of code can be implemented in approximately an
order of magnitude less code~\cite{geambasu_comet_2010}.

@@

\section{Services Built on Malacology}
\label{sec:services}
\label{services-built-on-malacology}

@@

In Section~\ref{evaluation} we quantify the trade-offs of throughput and
latency for an approach based on a round-robin batching mode, and compare this
mode to one in which the metadata server mediates access to the sequencer
state when in it is being shared among multiple clients.

@@

\section{Evaluation}
\label{evaluation}
We have conducted our evaluation on CloudLab as well as our own 20 node cluster. We follow the ``Popper Convention"~\cite{anonymous} so as to try and make our experiments as reproducible as possible. We have a GitHub repository with our source code,  experimental environment, configuration parameters, and workloads in a GitHub repository. Due to the double-blind policy, we have temporarily disabled the links to our graphs and experimental details.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{The sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput}
migrates to a new MDS immediately because its uses a policy designed for bursty
workloads. This is a trace of the same workload running twice: once with a
single MDS and once with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}
